RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-03-06 inst/doc/pubs/README.Rmd
update documentation

```{r}
f <- system.file("examples", "comp_analysis.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_trees(nexml) # or: as(nexml, "phylo")
plot(tr[[1]])
```

@@

```{r}
library(geiger)
fitContinuous(tree, traits[[1]])
fitDiscrete(tree, traits[[2]])
```

>>>>

```{r}
f <- system.file("examples", "comp_analysis.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_trees(nexml) # or: as(nexml, "phylo")
plot(tr)
```

@@

```{r}
library(geiger)
fitContinuous(tree, traits[1])
fitDiscrete(tree, traits[2])
```
